### 2024-11-26 paper/eval.tex
Add machine spec

We define the syntax and semantics of Wasm manually using the DSL.
The DSL is translated into AL, which serves as a Wasm interpreter that
faithfully follows the written specification.
To ensure correctness of the specification, we run this Wasm interpreter
against the execution tests from the official Wasm test suite.
The execution tests check whether the execution of a Wasm program produces
expected values or errors.
Tests related to inifinite loop detection are excluded, as the specification
does not define this behavior.
The results demonstrate that the interpreter successfully pass all 51,549 tests in 70
seconds on \red{(lambda 9)}.
Passing all the tests ensures the correctness of the specification.

% 7 + 3 + ??? + 44
\section{RQ2: Generality}
We evaluate AL's generality by applying SpecTec to eight proposals prepared for
inclusion in the next version of Wasm: typed function references
~\cite{proposal-fr}, garbage collection~\cite{propsal-gc}, tail calls
~\cite{proposal-tc}, multiple memories~\cite{proposal-mm}, extended constant
expressions~\cite{proposal-ec}, memory64~\cite{proposal-m64}, relaxed SIMD
~\cite{proposal-rs}, exception handling~\cite{proposal-eh}.
This proposals add or modify ??? Wasm instructions.
In particular, the garbage collection proposal adds substantial complications
to the Wasm type system, and the exception handling proposal introduces a new
context, \textit{handler}.
Notably, specifying all eight proposals in AL requires only trivial
adjustments, such as adding a handler case to the context.

>>>>

We define the syntax and semantics of Wasm manually using the DSL.
The DSL is translated into AL, which serves as a Wasm interpreter that
faithfully follows the written specification.
To ensure correctness of the specification, we run this Wasm interpreter
against the execution tests from the official Wasm test suite.
The execution tests check whether the execution of a Wasm program produces
expected values or errors.
Tests related to inifinite loop detection are excluded, as the specification
does not define this behavior.
The results demonstrate that the interpreter successfully pass all 51,549 tests
in 70 seconds on a machine running Ubuntu 18.04.3 LTS, equipped with an Intel
Core i7-6700K processor (6th generation) and 8GB of Samsung DDR4 PC4-17000
memory.
Passing all the tests ensures the correctness of the specification.

% 7 + 3 + ??? + 44
% TODO: Fill number
% TODO: Add cite
\section{RQ2: Generality}
We evaluate AL's generality by applying SpecTec to eight proposals prepared for
inclusion in the next version of Wasm: typed function references
~\cite{proposal-fr}, garbage collection~\cite{propsal-gc}, tail calls
~\cite{proposal-tc}, multiple memories~\cite{proposal-mm}, extended constant
expressions~\cite{proposal-ec}, memory64~\cite{proposal-m64}, relaxed SIMD
~\cite{proposal-rs}, exception handling~\cite{proposal-eh}.
This proposals add or modify ??? Wasm instructions.
In particular, the garbage collection proposal adds substantial complications
to the Wasm type system, and the exception handling proposal introduces a new
context, \textit{handler}.
Notably, specifying all eight proposals in AL requires only trivial
adjustments, such as adding a handler case to the context.
